A thesis draft

### 2018-11-20 res/sections/08-Background.tex
Rewrite some part on vibes and add reference to the website

Fields are:
\begin{description}
  \item[Version]: This field is used to set the version of the header, used for
  ensuring backward compatibility through different NSH definitions;
  \item[0 bit]: Bit set only in case of orchestration or management packets, and
  must not be changed by the SFC;
  \item[TTL]: Time To Live, indicate the maximum number of hops among SFF and
  its initial value should be configurable by the control plane. At each hop it
  must be decremented to 1 until 0: in the latter case the packet must be
  discarded. The default value is 63. This field is useful in loop prevention
  mechanism. The default value is 63;
  \item[Length]: the total length of the header (in 4-byte words), including
  the \texttt{Fixed-Length Context Header} in NSH type 0x1 or the
  \texttt{Variable-Length Context Header} in NSH type 0x2. In case of variable
  length header data must be padded to a multiple of 4;
  \item[Unassigned bits]: unassigned bits for future usages;
  \item[MD]: Metadata Type, indicate the type of the NSH. Values that now
  accepted are \texttt{0x0} that is a reserved value and if set the packet must
  be discarded, \texttt{0x1} indicate that context header length is
  fixed~\ref{subsubsec:background:flch}, \texttt{0x2} indicate that context
  header length is variable~\ref{subsubsec:background:vlch} and \texttt{0xF} for
  testing purposes (if not part of the experiment the packet must be discarded).
  Base header length and Service Path Header have always the same size;
  \item[Next Protocol]: indicates the protocol type of encapsulated data
  (protocols codes can be found at~\cite{rfc8300}).
\end{description}

@@

\begin{description}
  \item[Service Path Identifier (SPI)]: 24 bits, identify unambiguously an SFP.
  The first classifier have to set it;
  \item[Service Index (SI)]: 8 bits, provide location within the SFP. Initially
  must be set to 255 and it must be decremented on each hop.
\end{description}

@@

\begin{description}
  \item[Metadata Class (MD Class)]: field used in order to provide hierarchical
  namespaces for standards, vendors or other scopes;
  \item[Type]: indicates the type of metadata, depending on the MD Class;
\end{description}

@@

\section{The VIBES project}

 This thesis is part of the VIBES project\todo{Talk about VIBES project, add
   some reference, explain what it is.}, where the necessity for better TCP/IP
 transmission through satellite connections is the main requirement. To reach
 this goal, the project specifications suggest to exploit the 5G incoming
 technology and use the NFV-MANO architecture to perform first packets
 elaboration and performance improvement and finally TCP/IP satellite chunk
 optimization with the Performance Enhancing Proxy (PEP). The VIBES project
 proposed five technical requirements:
\begin{enumerate}
 \item Analysis of the applicability of current and new Internet protocols in
   the proposed VNF-PEP architecture
 \item Implementation of a VNF-PEP prototype
 \item Building of a PoC test platform
 \item VNF-PEP validation and performance tests on 5G use-cases
 \item Demonstration test-bed management
\end{enumerate}

@@

\subsection{VNF-PEP architecture and internet protocols}

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet encapsulation present itself as the only feasible solution:
every packet incoming in the VNFs has already been encapsulated by a generic
packet encapsulator/decapsulator,
\todo{Also I think that the main purpose of UDP encapsulation is not to hide 
the protocol used on the edges but 1) use a ``quick protocol to exchange data 
among VNFs and 2) we are hiding the path not the protocol itself. As we were 
discussing, we are creating some sort of proxy, so the aim will be the same 
even if we support a plethora of protocols.''} making the whole architecture 
independent from the protocol a particular flux of data. To achieve this, 
several solutions have been studied, and at the end packet encapsulation with 
TCP split (for TCP sessions) have been chosen. The rationale that guided us on 
this choice is described in Chapter~\ref{chap:vnf_ns_impl}. \todo{Update 
reference with the section of the explanation}

\subsection{VNF-PEP prototype}

Since the requirement for the whole system (MANO+PEP) were too challenging, the 
goal shifted into creating a MANO test-bed and a working NFVI, excluding PEP. 
The VNF architecture was shaped following the container orchestrator we decided 
to use. An more detailed architectural implementation can be found at 
Chapter~\ref{chap:archimpl}.

\vspace{0.5cm}

Starting with the first step of creating a MANO able to process incoming data
packets through VNF functions, we encountered that many networking tools already
present in the market required some tweaking and some integration, shifting our
goal to create a complete European Telecommunications Standards Institutes
(ETSI) Management and orchestrator (MANO) test-bed instead, following the
specifications suggested in the RFC 7665, thus implementing only the first three
requisites, without digging in the satellite data flow optimization. In
particular, we discovered how, these tools, were suitable to create ETSI MANO
and VNFs using virtual machine or exploiting cloud technologies, while they were
not designed with enough flexibility an integration with Docker. In the next
chapter we are going to take a deep analysis of the cited technologies 
(Section~\ref{chap:prjan:sec:tech}, in order to provide to the reader enough 
context to be able to understand our design choices we are going to describe 
later.

\noindent With this in mind, we performed a requirements analysis described in
the next chapter.\todo{This should be put at the end of the introduction.}

>>>>

Fields are:
\begin{description}
  \item[Version:] This field is used to set the version of the header, used for
  ensuring backward compatibility through different NSH definitions;
  \item[0 bit:] Bit set only in case of orchestration or management packets, and
  must not be changed by the SFC;
  \item[TTL:] Time To Live, indicate the maximum number of hops among SFF and
  its initial value should be configurable by the control plane. At each hop it
  must be decremented to 1 until 0: in the latter case the packet must be
  discarded. The default value is 63. This field is useful in loop prevention
  mechanism. The default value is 63;
  \item[Length:] the total length of the header (in 4-byte words), including
  the \texttt{Fixed-Length Context Header} in NSH type 0x1 or the
  \texttt{Variable-Length Context Header} in NSH type 0x2. In case of variable
  length header data must be padded to a multiple of 4;
  \item[Unassigned bits:] unassigned bits for future usages;
  \item[MD:] Metadata Type, indicate the type of the NSH. Values that now
  accepted are \texttt{0x0} that is a reserved value and if set the packet must
  be discarded, \texttt{0x1} indicate that context header length is
  fixed~\ref{subsubsec:background:flch}, \texttt{0x2} indicate that context
  header length is variable~\ref{subsubsec:background:vlch} and \texttt{0xF} for
  testing purposes (if not part of the experiment the packet must be discarded).
  Base header length and Service Path Header have always the same size;
  \item[Next Protocol:] indicates the protocol type of encapsulated data
  (protocols codes can be found at~\cite{rfc8300}).
\end{description}

@@

\begin{description}
  \item[Service Path Identifier (SPI):] 24 bits, identify unambiguously an SFP.
  The first classifier have to set it;
  \item[Service Index (SI):] 8 bits, provide location within the SFP. Initially
  must be set to 255 and it must be decremented on each hop.
\end{description}

@@

\begin{description}
  \item[Metadata Class (MD Class):] field used in order to provide hierarchical
  namespaces for standards, vendors or other scopes;
  \item[Type:] indicates the type of metadata, depending on the MD Class;
\end{description}

@@

\section{The VIBES project}
This thesis is part of the VIBES project~\cite{vibesesa}, whose main requirement
is to enhance the performance of end-to-end IP based that involves satellite
connections. To reach this goal, the project specifications suggest to exploit
the 5G incoming technology and use the NFV-MANO architecture to perform first
packets elaboration and performance improvement and finally TCP/IP satellite
chunk optimization with the Performance Enhancing Proxy (PEP). The VIBES project
proposed five technical requirements:
\begin{enumerate}
  \item Analysis of the applicability of current and new Internet protocols in
  the proposed VNF-PEP architecture
  \item Implementation of a VNF-PEP prototype
  \item Building of a PoC test platform
  \item VNF-PEP validation and performance tests on 5G use-cases
  \item Demonstration test-bed management
\end{enumerate}

@@

\subsection{VNF-PEP architecture and internet protocols}
VNF-PEP are the softwarization of usual PEP technology. One of the sake of the
project is to research and include this technology in the usual VNF ecosystem to
include without change satellite communications to the SFC. The architecture of
the systems will be based on clusters of containers whose management and
orchestration will follows the ETSI MANO architecture and SDN principles. Thanks
to VNF-PEP will be possible to dynamically take decisions on how to optimize a
certain communication.

%The analysis of this topic revealed to be trivial: since internet has many
%different protocols that would become infeasible to support all of them at the
%same time, packet encapsulation present itself as the only feasible solution:
%every packet incoming in the VNFs has already been encapsulated by a generic
%packet encapsulator/decapsulator,
%\todo{Also I think that the main purpose of UDP encapsulation is not to hide 
%the protocol used on the edges but 1) use a ``quick protocol to exchange data 
%among VNFs and 2) we are hiding the path not the protocol itself. As we were 
%discussing, we are creating some sort of proxy, so the aim will be the same 
%even if we support a plethora of protocols.''} making the whole architecture 
%independent from the protocol a particular flux of data. To achieve this, 
%several solutions have been studied, and at the end packet encapsulation with 
%TCP split (for TCP sessions) have been chosen. The rationale that guided us on 
%this choice is described in Chapter~\ref{chap:vnf_ns_impl}. \todo{Update 
%reference with the section of the explanation}
%
%\subsection{VNF-PEP prototype}
%
%Since the requirement for the whole system (MANO+PEP) were too challenging, the 
%goal shifted into creating a MANO test-bed and a working NFVI, excluding PEP. 
%The VNF architecture was shaped following the container orchestrator we decided 
%to use. An more detailed architectural implementation can be found at 
%Chapter~\ref{chap:archimpl}.
%
%\vspace{0.5cm}
%
%Starting with the first step of creating a MANO able to process incoming data
%packets through VNF functions, we encountered that many networking tools already
%present in the market required some tweaking and some integration, shifting our
%goal to create a complete European Telecommunications Standards Institutes
%(ETSI) Management and orchestrator (MANO) test-bed instead, following the
%specifications suggested in the RFC 7665, thus implementing only the first three
%requisites, without digging in the satellite data flow optimization. In
%particular, we discovered how, these tools, were suitable to create ETSI MANO
%and VNFs using virtual machine or exploiting cloud technologies, while they were
%not designed with enough flexibility an integration with Docker. In the next
%chapter we are going to take a deep analysis of the cited technologies 
%(Section~\ref{chap:prjan:sec:tech}, in order to provide to the reader enough 
%context to be able to understand our design choices we are going to describe 
%later.
%
%\noindent With this in mind, we performed a requirements analysis described in
%the next chapter.\todo{This should be put at the end of the introduction.}
%
